Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-22 paper/paper.Rmd
update use of data to be locked at 1st Sept 2022 #1

We extracted forecasts and data on notified weekly COVID-19 cases from the European forecasting hub [@Sherratt2022-ue; @EuroHub] from the 15th of January 2022 to the 19th of July 2022 for the ensemble model (referred to as the `EuroCOVIDhub-ensemble` by the hub team) and the surrogate model (submitted as `epiforecasts-weeklygrowth`).
We included all locations covered by the European forecasting hub which were 32 European countries, including all countries of the European Union and European Free Trade Area, and the United Kingdom.
Data on notified weekly cases was originally sourced from the Johns Hopkins University (JHU) curated data repository [@REF].
We used the latest available observed data as of the 20th of August 2022. As observations are subject to revisions this means that the data used to produce forecasts for a given date may not reflect the data used for evaluation.
This follows the practice of the European forecasting hub project in treating the latest available data as the forecast target regardless of the number of potential data revisions [@Sherratt2022-ue].
Incidence was aggregated over the Morbidity and Mortality Weekly Report (MMWR) epidemiological week definition of Sunday through Saturday.

>>>>

We extracted forecasts and data on notified weekly COVID-19 cases from the European forecasting hub [@Sherratt2022-ue; @EuroHub] from the 15th of January 2022 to the 19th of July 2022 for the ensemble model (referred to as the `EuroCOVIDhub-ensemble` by the hub team) and the surrogate model (submitted as `epiforecasts-weeklygrowth`).
We included all locations covered by the European forecasting hub which were 32 European countries, including all countries of the European Union and European Free Trade Area, and the United Kingdom.
Data on notified weekly cases was originally sourced from the Johns Hopkins University (JHU) curated data repository [@JHU].
We used the latest available observed data as of the 1st of September 2022 (commit `f6922c3e4bdcb055abcbba8e73472afacac4cf40` from [@EuroHubGitHub]).
Incidence was aggregated over the Morbidity and Mortality Weekly Report (MMWR) epidemiological week definition of Sunday through Saturday.
As observations are subject to revisions this means that the data used to produce forecasts for a given date may not reflect the data used for evaluation.
To account for this we followed the practice of the European forecasting hub project in excluding forecasts made using anomolous truth data in the week of the forecasts production and excluding forecasts for target weeks with anomolous data [@Sherratt2022-ue].
We defined anomolous data based on the implementation used by the [@EuroHub] where a datapoint is considered anomolous if a future revision alters it by more than 5%.
